---
title: "Summer Camps"
author: "DK"
date: "2025-08-29"
draft: yes
categories: [camps]
---

> That's the last camp out ever

After a streneous weekend

Having 3 sons, went to my share of campouts

------------------------------------------------------------------------

For an immigrant son, that was our summer vacation

I either participated or as participant's father

```{r}
library(leaflet)

leaflet() %>% addTiles() %>% addMarkers(lng = -79.466412641026, lat = 37.966739574143794, popup = "Goshen Scout Reservation")


```

The camp caretaker said the Maple Dell is now used by Cub Scouts. Not much use.

Much memories created. Fathers adjusting their obligations and checking their commitments to be with their sons.

Real wealth of a nation. Fathers spending time with their sons. Adults sacrificing their time to be with young men for a whole week.

```{r}
library(leaflet)

leaflet() %>% addTiles() %>% addMarkers(lng = -111.69274405731123, lat = 39.97265970612137, popup = "Camp Maple Dell, BSA")
```
